Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-01-19 bbbq_article.tex
Add scripts
Add selenoproteins

There are multiple computational tools developed to predict which
parts of membrane proteins are TMH.
In 2001, multiple tools to do so have been compared (\cite{moller2001evaluation}),
of which TMHMM (\cite{krogh2001predicting}) turned out to be the best.
TMHMM is used in the previous study (\cite{bianchi2017}),
yet TMHMM itself has a restrictive software license and is nearly two
decades old. 
Inspired on TMHMM, many other tools followed, such as 
Phobius (\cite{kall2004combined}),
ConPred II (\cite{arai2004conpred}),
MEMSAT3 (\cite{jones2007improving})
and MetaTM (\cite{klammer2009metatm}).
The most recent FOSS tool is called PureseqTM (\cite{wang2019efficient}),
which is used in this study.

@@

@@

>>>>

There are multiple computational tools developed to predict which
parts of membrane proteins are TMH.
In 2001, multiple tools to do so have been compared (\cite{moller2001evaluation}),
of which TMHMM (\cite{krogh2001predicting}) turned out to be the best, 
as is used in the previous study (\cite{bianchi2017}).
TMHMM has a restrictive software license and is nearly two
decades old.
Due to this, also PureseqTM (\cite{wang2019efficient}),
is used in this study, which has been recently developed
and has a free software license.

@@

Both TMH prediction tools struggle with selenocysteine,
the 21st amino acid incorporated in human proteins.
The human reference proteome used contains 30 selenoproteins.
TMHMM gives a clear error message, due to which we removed
these selenoproteins from the analysis.
How PureseqTM deals with selenocysteine is unclear,
as it gives no error, nor is it mentioned anywhere,
nor do the authors respond to emails.
We assume PureseqTM ignores these residues.
In either case, we think that the effect of the 30 selenoproteins
on a proteome of 20600 proteins is only minor.

@@

\paragraph{Unclear handing of sequences with U}

Within the human reference proteome, there are 30 sequences that have a
selenocysteine (with the symbol 'U').
See \url{https://github.com/richelbilderbeek/bbbq_article/issues/158}.

\paragraph{Which reference proteome?}

See \url{https://github.com/richelbilderbeek/bbbq_article/issues/155}.
